Modern Graph Generators: A Survey

### 2018-11-08 generators_GraphDatabases.tex
Sherif Changes

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud computing systems. Its intent is to automate
the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and is composed of a workload generator client and a package of standard workloads that cover interesting parts of the performance space.
The workload generator of YCSB supports definition of new workload types. XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties. A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

>>>>

\paragraph{XGDBench} XGDBench~\cite{Dayarathna:2014:GDB:2676904.2676939} is an extensible graph database benchmarking platform for cloud-based systems. Its intent is to automate
the process of graph database benchmarking in the cloud by focusing on a graph database application for social networking services. It extends the Yahoo! Cloud Multiplicative Attribute (MAG) Graph Serving Benchmark (YCSB)~\cite{Cooper:2010:BCS:1807128.1807152} and \iffalse consists of of a workload generator client and\fi provides a package of standard workloads that cover interesting parts of the performance space.
\iffalse In particular, the workload generator of YCSB supports definition of new workload types.\fi In particular, the workload of XGDBench involves basic operations such as read / insert / update / delete an attribute, loading of the list of neighbors and BFS traversal. Using the generators, 7 workloads are created, such as update heavy, read mostly, short range scan, traverse heavy etc.
The data model of XGDBench is a simplified version of the Multiplicative Attribute Graph (MAG)~\cite{Kim2010} model, a synthetic graph model for attribute graphs which models the interactions between the network structure and the node attributes.
The generated graphs are thus in MAG format, with power-law degree distribution closely simulating real-world social networks.
The simplified MAG algorithm accepts the number of vertices of the generated graph, the number of attributes per vertex, a threshold value for random initialization of attributes, an edge affinity threshold value that determines whether there is an edge between two vertices, and an affinity matrix. \iffalse It has been proven that MAG generates graphs with both analytically tractable and statistically interesting properties.\fi A multi-threaded version of the graph generator that generates large graphs on multi-core systems faster was implemented too.

### 2018-11-08 generators_LinkedData.tex
Sherif Changes

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP as a domain for the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated documents mirror key characteristics and distributions found in the original DBLP database. The data mimics natural correlations between entities, such as power law distributions (found in the citation system or the distribution of publications among authors) and limited growth curves (e.g., the increasing number of venues and publications over time). All random functions of the generator base on a fixed seed which makes data generation deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations, RDF access paths, typical RDF constructs etc.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that were issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous (e.g., DBpedia version 3.6, for example, contains 289,016 classes of which 275 classes belong
to the DBpedia ontology) and various datatypes and object references of different types are
used in property values. Hence, they propose a generic SPARQL benchmark creation methodology based on a flexible data generation mimicking an input data source, query-log mining, clustering, and SPARQL feature analysis. The proposed dataset creation process starts with an input dataset. Datasets of multiple sizes of the original data are created by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity. The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, which cover most commonly used SPARQL features and are used to generate the actual benchmark queries by parametrization.

@@

\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in representing the real RDF datasets and are mostly relational-like. Hence, they propose a benchmark for challenging query processing over real graphs~\cite{sib}. It simulates an RDF backend of a social network site, in which users and their interactions form a social graph of social activities such as writing posts, posting comments, creating/managing groups, etc. The distribution of generated data on each relation conforms to the data distribution analyzed over real-world social networks. Association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on publicly available linked data sets covering a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark introduces two classes of query features -- structural and data-driven -- and performs an in-depth analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to test the strengths and weaknesses of different physical design choices employed by RDF systems. The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which computes the structural and data-driven features of the generated data and workload. For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which takes any RDF dataset as a template and generates a set of synthetic datasets with similar characteristics, required size scaling factor $s$ and (node) degree scaling factor $d$. A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity. A query generation process is proposed to generate 5 types of queries (node queries, edge queries, star queries, path queries, and subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is able to generate benchmarks from a set of queries (in particular from query logs) by selecting prototypical queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark considers a media or a publishing organization that deals with large volumes of streaming content, namely news, articles or  ``media assets''. This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets. The data generator models three types of relations in produced synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  consisting of interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distribution techniques for generating entities: Gaussian distribution and Zipf's power-law distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.

>>>>

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which is based on the DBLP  the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated datasets follow the key characteristics of the original DBLP dataset. In particular, the data mimics the correlations between entities. All random functions of the generator is based on a fixed seed that ensures the data generation process to be deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations such as RDF access paths and typical RDF constructs.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The degree of structuredness of a dataset $D$ with respect to a type $T$ is based on  the regularity of instance data in $D$ on conforming to type $T$. The type system is extracted from the data set by finding the RDF triples that have property  \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extract type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset associated with a required level of structuredness and size (smaller than the size of the original data), and exploits the input documents as a seed to generate a subset of the original data with the target structuredness and size. In addition, they show that structuredness and size mutually influence each other.

\paragraph{DBPSB} DBpedia SPARQL Benchmark (DBPSB)\footnote{\url{http://aksw.org/Projects/DBPSB.html}} proposed at the University of Leipzig is based on queries that have been issued by humans and applications
against existing RDF data~\cite{Morsey2011,Morsey:2012:UBR:2900929.2901031}. In addition, the authors argue that benchmarks like LUBM, BSBM, or SP$^2$Bench resemble relational database benchmarks involving relational data structures with few and homogeneously structured classes, whereas RDF knowledge bases are increasingly heterogeneous. For example, DBpedia version 3.6 consists of 289,016 classes of which 275 classes are defined based on the DBpedia ontology. In addition, different datatypes and object references of various types are
used in property values. Hence, they presented a generic SPARQL benchmark creation approach which is based on a flexible data generation mechanism that mimics the input data source. The proposed dataset creation process starts with an input dataset. Multiple Datasets with different sizes  are then generated by duplicating all triples and changing their namespaces.  For generating smaller datasets, an appropriate fraction of all triples is selected randomly or by sampling across classes in the dataset. \iffalse The goal of the query analysis and clustering is to detect prototypical queries on the basis of their frequent usage and similarity.\fi The methodology is applied on the DBpedia SPARQL endpoint and a set of 25 SPARQL query templates is derived, that cover the most commonly used SPARQL features.

@@

\paragraph{SIB} The developers of the Social Network Intelligence BenchMark (SIB)\footnote{\url{https://www.w3.org/wiki/Social_Network_Intelligence_BenchMark}} based the design of their benchmark based on the claim that existing benchmarks are limited in reflecting the characteristics of the real RDF datasets and are mostly relational-like. Hence, they proposed a benchmark for  query processing over real graphs~\cite{sib}. The proposed benchmark simulates an RDF backend of a social network site where users and their interactions form a social graph of social activities such as creating/managing groups, writing posts and posting comments. The distribution of generated data on each relation follows the data distribution inferred from real-world social networks. In addition, association rules are included in order to convey the real-world data correlation into synthetic data. The  generated data is linked with the RDF datasets from DBpedia. The benchmark specification contains 3 query mixes -- interactive, update, and analysis -- expressed in SPARQL 1.1 Working Draft.

\paragraph{Geographica} The Geographica benchmark\footnote{\url{http://geographica.di.uoa.gr/}} has been designed to target the area of geospatial data~\cite{DBLP:conf/semweb/GarbisKK13} and respective SPARQL extensions GeoSPARQL~\cite{battle2012enabling} and stSPARQL~\cite{koubarakis2010modeling}. The benchmark involves a real-world workload based on openly available datasets that cove a range of geometry types (e.g., points, lines, polygons) and  a synthetic workload. In the former case there is a (1) a micro benchmark that tests primitive spatial functions (involving 29 queries) and (2) macro benchmark that tests the performance of RDF stores in typical application scenarios like reverse geocoding or map search and browsing (consisting of 11 queries). In the latter case of a synthetic workload the generator produces synthetic datasets of various sizes that corresponds to an ontology based on OpenStreetMap (i.e., states in a country, land ownership, roads and  points of interest) and instantiates query templates. The spatial extent of the land ownership dataset constitutes a uniform grid of $n \times n$ hexagons, whereas the size of each dataset is given relatively to $n$. The synthetic workload generator produces SPARQL queries corresponding to spatial selection and spatial joins by instantiating 2 query templates.

\paragraph{WatDiv} The Waterloo SPARQL Diversity Test Suite (WatDiv)\footnote{\url{http://dsg.uwaterloo.ca/watdiv/}} developed at the University of Waterloo provides stress testing tools to address the observation that existing SPARQL benchmarks are not suitable for testing systems for diverse queries and varied workloads~\cite{Aluc:2014:DST:2717213.2717229}. The benchmark introduces two classes of query features -- structural and data-driven -- and performs a detailed analysis on existing SPARQL benchmarks (LUBM, BSBM, SP$^2$Bench, and DBPSB) using the two classes of query features. The structural features involve triple pattern count, join vertex count, join vertex degree, and join vertex count. The data-driven features involve result cardinality and several types of selectivity. The analysis of the four benchmarks reveals that they are not sufficiently diverse to evaluate the strengths and weaknesses of the various physical design alternatives that have been implemented by the different RDF systems. The proposed solution, WatDiv, involves (1) a data generator which generates scalable datasets according to the WatDiv schema, (2) a query template generator which traverses the WatDiv schema and generates a diverse set of query templates, (3) a query generator which instantiates the templates with actual RDF terms from the dataset, and (4) a feature extractor which extracts the structural features of the generated data and workload. %For the study in the paper the authors generated 12,500 test queries from 125 query templates.

\paragraph{RBench} RBench~\cite{Qiao:2015:RAR:2723372.2746479} is an application-specific benchmark which receives any RDF dataset as an input and produces as an output a set of datasets, that have similar characteristics of the input dataset, using size scaling factor $s$ and (node) degree scaling factor $d$. \iffalse A generated benchmark dataset is considered similar to the given dataset if their values for the dataset evaluation metrics and query evaluation times for different techniques are similar. Three evaluation metrics are utilized for this purpose: dataset coherence (i.e., a measure how uniformly predicates are distributed among the same type/class), relationship specialty (i.e., the number of occurrences of the same predicate associated with each resource), and literal diversity.\fi A query generation process has been implemented to produce 5 different types of queries (edge-based queries, node-based queries, path queries, star queries, subgraph queries) for any generated data. The benchmark project FEASIBLE~\cite{Saleem2015} is also an application-specific benchmark; however, contrary to RBench, it is designed to produce benchmarks from a set of queries (in particular from query logs) by relying on example queries of a user-defined
size from the input set of queries.

\paragraph{LDBC}  The Linked Data Benchmark Council\footnote{\url{http://ldbcouncil.org/industry/organization/origins}} (LDBC)~\cite{Angles:2014:LDB:2627692.2627697} is a result of a (closed) EU project that brought together a community of academic researchers and industry that had the main objective of developing an open source, yet industrial grade benchmarks for graph and RDF databases. \iffalse The following three benchmarks were developed and are currently maintained.\fi In the Semantic Web domain, the project released the Semantic Publishing Benchmark (SPB)~\cite{spb} that has been inspired by the Media/Publishing industry (namely BBC\footnote{\url{http://www.bbc.com/}}). The application scenario of this benchmark simulates a media or a publishing organization that handles large amount of streaming content (e.g., news, articles). \iffalse This content is enriched with metadata that describes it and links it to reference knowledge -- taxonomies and databases that include relevant concepts, entities and factual information. The SPB data generator produces scalable in size synthetic large data. Synthetic data consists of a large number of annotations of media assets that refer entities found in reference datasets.\fi The data generator mimics three types of relations in the generated synthetic data: clustering of data, correlations of entities, and random tagging of entities. Two workloads are provided: (1) basic, involving an interactive query-mix querying the relations between entities in reference data, and (2) advanced,  focusing on interactive and analytical query-mixes. The LDBC has designed two other benchmarks: the Social Network Benchmark (SNB)~\cite{Erling:2015:LSN:2723372.2742786} for the social network domain  (see Section~\ref{sec:generators_socialnetworks}) and Graphalytics~\cite{Iosup:2016:LGB:3007263.3007270}   for the analytics domain.% (see Section~\ref{sec:generators_analytics}).

\paragraph{LinkGen} LinkGen is a synthetic linked data generator that has been designed to generate RDF datasets for a given vocabulary~\cite{10.1007/978-3-319-46547-0_12}. The generator is designed to receive a vocabulary as an input  and supports two statistical distributions for generating entities: Gaussian distribution and Zipf's power-law distribution. LinkGen can augment the generated data with inconsistent and noisy  data such as writing two conflicting values for a given datatype property,  adding triples with syntactic errors, adding wrong statements by assigning them with invalid domain and creating instances with no type information. The generator is also designed with  an option to inter-link the generated instances with real ones given that the user provides entities from real datasets. The datasets can be generated in any of of two modes: on-disk and streaming.
